

To write the given worksheet in LaTeX, follow the steps below:

1. Start by defining the document class and language. In this case, we want to write a document in Spanish. Add the following lines at the beginning of your LaTeX document:

\documentclass[spanish]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}

2. Add the necessary packages for mathematical expressions and symbols. Include the following lines in your LaTeX document:

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

3. Begin the document with the \begin{document} command and end it with the \end{document} command. Your LaTeX code should now look like this:

\documentclass[spanish]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\begin{document}

4. Start writing the content of the worksheet. Begin by adding a title for the worksheet. For example:

\title{Problemas de Palabras - Grado 5}
\author{Tú Nombre}
\date{}

\maketitle

5. Use the \section{} command to separate each problem. For example, to write the first problem, use:

\section{Problema 1}

A piece of ribbon is $y$ cm long. Ashley cut it into 4 equal pieces to do her 4 sisters’ hair. Write the expression for the amount of ribbon used for each sister.

6. Next, write the solution for each problem using the \textbf{} command to make important words bold, and the $...$ command to write mathematical symbols. For example, for the first problem, write:

\textbf{Solución:}

Cada hermana recibe $\frac{y}{4}$ cm de la cinta.

7. Repeat steps 5 and 6 for the remaining problems. Here's an example for problem 2:

\section{Problema 2}

Margaret has 16 yards of fabric, and she is making dresses for $z$ dolls. Write the expression for the length of fabric used for each doll.

\textbf{Solución:}

Cada muñeca usa $\frac{16}{z}$ yards de tela.

8. Finally, end the document with the \end{document} command.

\end{document}

And that's it! You have successfully created a LaTeX document in Spanish with step-by-step guides to solve the math problems in the given worksheet.

